Dynamics of Laterally Propagating Flames in X-ray Bursts. II. Realistic Burning \& Rotation

### 2020-08-24 xrb2/paper.tex
more notes

lateral profiles of X vs distance behind the flame

vertical profiles of the atmosphere behind the flame---how does it compare to isentropic?

@@

>>>>

MZ: lateral profiles of X vs distance behind the flame; 
vertical profiles of the atmosphere behind the flame---how does it compare to isentropic?

@@

Don: look at ratio of enuc to e?
